# Abstract

This repository contains the SQL model of the _Ros_ database from version **3.1.2** to nowadays.

## Prepare the ros connection file

Create a *JSON* file named ```ros-db.json``` with content:

```json
{
  "host": "localhost",
  "port": "5432",
  "user": "xxx",
  "password": "xxx"
}
```

## Generate database metadata

```{r, warning = FALSE}
# Load sources
source("R/common_db_utils.R")
source("R/ros_db_metadata.R")
# Generate Ros dtabase metatadata files
generate_db_metadata(extract_db_metadata(schemas = c(ROS_SCHEMAS$ALL, ROS_SCHEMAS$CODE_LIST), connection_provider = connect_to_ros), output_directory = DB_METADATA_DIRECTORY)
# Generate Ros database shell dependencies table
ros_db_generate_shell_dependencies(root_directory = DB_METADATA_DIRECTORY)
```
## Update comments on database

```{r, warning = FALSE}
# Load sources
source("R/common_db_utils.R")
source("R/ros_db_metadata.R")
# Update for the hole Ros database
ros_update_queries <- apply_comments_on_db(root_directory = DB_METADATA_DIRECTORY, connection_provider = connect_to_ros)
```
## Generate database metadata report

```{r, warning = FALSE}
# Load sources
source("R/common_db_utils.R")
source("R/common_db_report.R")
source("R/ros_db_metadata.R")
# Generate documentation report of the hole Ros database
ros_db_metadata_generate_report(domain = "ALL", timestamp = DEFAULT_TIME_STAMP)
# Generate documentation report of the PS domain
ros_db_metadata_generate_report(domain = "PS", timestamp = DEFAULT_TIME_STAMP)
# Generate documentation report of the LL domain
ros_db_metadata_generate_report(domain = "LL", timestamp = DEFAULT_TIME_STAMP)
# Generate documentation report of the PL domain
ros_db_metadata_generate_report(domain = "PL", timestamp = DEFAULT_TIME_STAMP)
# Generate documentation report of the GN domain
ros_db_metadata_generate_report(domain = "GN", timestamp = DEFAULT_TIME_STAMP)
```
```{r, warning = FALSE}
# Load sources
source("R/common_db_utils.R")
source("R/common_db_report.R")
source("R/ros_db_metadata.R")
ros_db_metadata_generate_report(domain = "LL", timestamp = DEFAULT_TIME_STAMP)
```

## Generate missing index.html files in doc directory

```{r, warning = FALSE}
# Load sources
source("R/generate_indexes.R")

```

## Remove all views from Ros database on code list schemas
```{r,  warning = FALSE}
# Load sources
source("R/common_db_utils.R")
source("R/ros_db_metadata.R")
source("R/reference_data_synchronization.R")
generate_drop_views_script(connection_provider = connect_to_ros,
                           schemas = ROS_SCHEMAS$CODE_LIST,
                           output_file = "3.3.0/sql/2026-06-23/11_00_01_drop_code_lists_views.sql")

```
## Generate SQL script to synchronize missing code list from Reference data db to Ros db

```{r, warning = FALSE}
# Load sources
source("R/common_db_utils.R")
source("R/ros_db_metadata.R")
source("R/reference_data_db.R")
source("R/reference_data_synchronization.R")
schema_excluder <- function(schema) { schema %in% c("refs_legacy", "refs_socio_economics", "refs_mappings") }
generate_missing_code_list_tables_script(reference_data_connection_provider = connect_to_reference_data,
                                         ros_connection_provider = connect_to_ros,
                                         schema_excluder = schema_excluder,
                                         output_file = "./3.3.0/sql/2026-06-23/11_02_add_new_code_lists.sql")
```
## Generate SQL script to synchronize existing code list from Reference data db to Ros db (will also synchronize descriptions on table and columns)

```{r, warning = FALSE}
# Load sources
source("R/common_db_utils.R")
source("R/ros_db_metadata.R")
source("R/reference_data_db.R")
source("R/reference_data_synchronization.R")
table_excluder <- function(schema, table) { paste0(schema, ".", table) %in% c("refs_admin.fleet_to_flags_and_fisheries") }
tables_to_update <- load_db_metadata(output_directory = DB_METADATA_DIRECTORY)$dependencies[table_id %like% "refs_.+"][, `:=`(
  schema = mapply(function(x) { table_location$new(x)$schema() }, table_id),
  table = mapply(function(x) { table_location$new(x)$table() }, table_id))][mapply(function(s, t) { !table_excluder(s, t) }, schema, table), .(schema, table)]
schemas_to_file_prefix <- c(
  refs_admin = "11_05_01",
  refs_biology = "11_05_02",
  refs_data = "11_05_03",
  refs_fishery = "11_05_04",
  refs_fishery_config = "11_05_05",
  refs_gis = "11_05_06"
)
sorted_tables_to_update <- sort_code_list_tables_to_update(reference_data_connection_provider = connect_to_reference_data,
                                                           tables = tables_to_update)

generate_existing_code_list_upsert_script(reference_data_connection_provider = connect_to_reference_data,
                                          tables_to_update = sorted_tables_to_update,
                                          schemas_to_file_prefix = schemas_to_file_prefix,
                                          output_file_pattern = "./3.3.0/sql/2026-06-23/%s_update_code_lists_%s.sql")
```
